### 2021-02-18 evaluation.tex
Move a table label
Specify placement of a table
Add a placeholder for a simple model
Finalize the analysis of preprocessing time
by describing an upper bound for 80th percentile.

To generate a precedence for a problem,
\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit is only imposed on the Vampire run
and excludes the time taken by the recommender to generate the precedence.
\todo{MS: and if we don't, this would be the perfect place to summarize
how long the just described procedure took on an average problem,
or how it (roughly) scales with the graph/cnf/tptp\_file size.}
When run with 1 thread on 1000 problems,
\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
the preprocessing took 1 second on average and at most 5 seconds,
increasing linearly with the number of nodes of the graph representation of the problem.
\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
\todo{FB: Measure the times with joint recommender and TF restricted to 1 thread.
 Fix the numbers once we have a solid measurement.
 Add a comment with a reference to the data.}
 \todo{MS: To by bylo taky fajn!}

@@

\begin{table*}
\caption{
Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$.
Means and standard deviations over 5 runs are reported.
}
\centering
\begin{tabular}{l|ll|ll}

@@

@@

\end{tabular}
\label{tab:results}
\end{table*}
\todo{FB: Add links to Neptune runs?}
\todo{FB: Finalize results for function precedences.}
\todo{FB: Try to evaluate a recommender that uses both predicate and function models.}

>>>>

To generate a precedence for a problem,
\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit is only imposed on the Vampire run
and excludes the time taken by the recommender to generate the precedence.
\todo{MS: and if we don't, this would be the perfect place to summarize
how long the just described procedure took on an average problem,
or how it (roughly) scales with the graph/cnf/tptp\_file size.}
When run with 2 threads,
the preprocessing of a single problem
takes at most at most \num[round-mode=places,round-precision=2]{1.262744486} seconds
for \SI{80}{\percent} of the problems
according to data measured on a random sample of \num{1000} problems.
% Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
% VML-715
\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}

@@

\begin{table*}[h]
\caption{
Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$.
Means and standard deviations over 5 runs are reported.
}
\label{tab:results}
\centering
\begin{tabular}{l|ll|ll}

@@

Simple & ? & ? & ? & ? \\
% Final vector from PAAR paper: [0,0.429306921481749,0.57069307851825,0,0,0,0,0,0,0,0,0]
% Source: https://docs.google.com/spreadsheets/d/1HSsC7piUAtWt6uwA9SYOX5vmiF0Ab3Ae4FPyGsDALIg/edit#gid=99404775

@@

\end{tabular}
\end{table*}
\todo{FB: Add links to Neptune runs?}
\todo{FB: Finalize results for function precedences.}
\todo{FB: Try to evaluate a recommender that uses both predicate and function models.}

### 2021-02-18 main.tex
Use package hyperref
to decorate the PDF with hyperlinks and metadata.
Add results of preprocessing time including a chart
Finalize the analysis of preprocessing time
by describing an upper bound for 80th percentile.

@@

@@

>>>>

\usepackage{svg}

@@

\usepackage{hyperref}
\hypersetup{
pdftitle={Neural Precedence Recommender},
pdfauthor={Filip Bártek, Martin Suda},
pdfkeywords={saturation-based theorem proving, simplification ordering, symbol precedence, machine learning, graph convolutional network}
}

\usepackage{cleveref}

@@

\appendix

\section{Experiment details}

\begin{figure}[h]
\caption{The dependence of preprocessing time on the number of nodes in the problem graph on 1000 random validation problems}
\label{fig:preprocessing}
\centering
\includesvg[width=\textwidth]{preprocessing}
% Source: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit#gid=394425425&fvid=659935521
% Experiment: VML-715
\end{figure}
